\mytitle

### 2023-05-15 chapters/depsynth/intro.tex
Section names
Deambiguate section labels

\section{Introduction}

@@

We evaluate the effectiveness and utility of \depsynth
in a case study that applies it to a production key-value store
developed by a major commercial cloud provider.%
\footnote{Anonymized for double-blind review.}
We show that \depsynth can rapidly synthesize dependency rules for this storage system.
By comparing those rules to the key-value store's existing crash-consistency behavior,
we find that \depsynth achieves similar results to rules hand-written by experts,
and even corrects an existing crash-consistency issue in the system automatically.
We also show that dependency rules synthesized by \depsynth
generalize beyond the example litmus tests used for synthesis,
and that \depsynth can be used for storage systems beyond key-value stores.
% Finally, we show that an automated crash consistency approach
% supports rapid iteration by using \depsynth
% to \emph{re}-synthesize dependency rules
% after changing the underlying storage hardware (and thus the guarantees it offers).

@@

\noindent
The remainder of this paper is organized as follows.
\cref{s:overview} gives a walk-through of building a simple storage system with \depsynth.
\cref{sec:problem} defines the \depsynth programming model, including labeled writes and dependency rules.
\cref{sec:alg} describes the \depsynth synthesis algorithm for inferring dependency rules,
and \cref{s:impl} details \depsynth's implementation in Rosette.
\cref{sec:eval} evaluates the effectiveness of \depsynth.
\cref{s:related} discusses related work, and \cref{s:conclusion} concludes.\tighten

@@

The rest of this paper is organized as follows.
\autoref{s:overview} illustrates how developers use \depsynth to construct a basic crash consistent storage system.
\autoref{s:problem} formalizes the dependency rule synthesis problem.
\autoref{s:algorithm} presents the \depsynth algorithm for searching for rules over a set of litmus tests.
\autoref{s:impl} provides implementation details.
\autoref{s:eval} evaluates \depsynth.
\autoref{s:related} discusses related work.
\autoref{s:conclusion} concludes.
\fi

>>>>

\section{Overview}

@@

We evaluate the effectiveness and utility of \depsynth
in a case study that applies it to \shardstore~\cite{bornholt:s3},
a production key-value store used by the Amazon S3 object storage service.
We show that \depsynth can rapidly synthesize dependency rules for this storage system.
By comparing those rules to the key-value store's existing crash-consistency behavior,
we find that \depsynth achieves similar results to rules hand-written by experts,
and even corrects an existing crash-consistency issue in the system automatically.
We also show that dependency rules synthesized by \depsynth
generalize beyond the example litmus tests used for synthesis,
and that \depsynth can be used for storage systems beyond key-value stores.
% Finally, we show that an automated crash consistency approach
% supports rapid iteration by using \depsynth
% to \emph{re}-synthesize dependency rules
% after changing the underlying storage hardware (and thus the guarantees it offers).

@@

\noindent
The remainder of this paper is organized as follows.
\cref{depsynth:s:overview} gives a walk-through of building a simple storage system with \depsynth.
\cref{sec:problem} defines the \depsynth programming model, including labeled writes and dependency rules.
\cref{sec:alg} describes the \depsynth synthesis algorithm for inferring dependency rules,
and \cref{s:impl} details \depsynth's implementation in Rosette.
\cref{sec:eval} evaluates the effectiveness of \depsynth.
\cref{s:related} discusses related work, and \cref{s:conclusion} concludes.\tighten

@@

The rest of this paper is organized as follows.
\autoref{depsynth:s:overview} illustrates how developers use \depsynth to construct a basic crash consistent storage system.
\autoref{s:problem} formalizes the dependency rule synthesis problem.
\autoref{s:algorithm} presents the \depsynth algorithm for searching for rules over a set of litmus tests.
\autoref{s:impl} provides implementation details.
\autoref{s:eval} evaluates \depsynth.
\autoref{s:related} discusses related work.
\autoref{s:conclusion} concludes.
\fi

### 2023-05-15 chapters/depsynth/problem.tex
Deambiguate section labels

\begin{example}\label{sec:problem:example}
Consider the \texttt{SingleEntry_TwoAppend} litmus test from \cref{s:overview}.
Interpreting the initial and main programs gives two traces:
%
\begin{align*}
    \interpret{P_\emph{initial}} &= [\texttt{write}(1, \texttt{to_block}((0, 42)), \langle \textsf{log}, 0 \rangle), \\
                                 &\quad\ \  \texttt{write}(0, \texttt{to_block}((1, 2)),  \langle \textsf{superblock}, 0 \rangle)] \\
    \interpret{P_\emph{main}}    &= [\texttt{write}(2, \texttt{to_block}((1, 81)), \langle \textsf{log}, 1 \rangle), \\
                                 &\quad\ \  \texttt{write}(0, \texttt{to_block}((1, 3)),  \langle \textsf{superblock}, 1 \rangle), \\
                                 &\quad\ \  \texttt{write}(3, \texttt{to_block}((2, 37)), \langle \textsf{log}, 2 \rangle), \\
                                 &\quad\ \  \texttt{write}(0, \texttt{to_block}((1, 4)),  \langle \textsf{superblock}, 2 \rangle)]
\end{align*}
%
Let $\vec{s} = [s_1, s_2, s_3, s_4]$ be a crash schedule for $P_\emph{main}$.
Applying the two synthesized rules from \cref{s:overview}
restricts the valid crash schedules (\cref{def:valid-schedule}):
%
\begin{itemize}
\item $\deprule{\textsf{superblock}}{\textsf{log}}{=}$ requires $s_2 \rightarrow s_1$ and $s_4 \rightarrow s_3$.
\item $\deprule{\textsf{superblock}}{\textsf{superblock}}{>}$ requires $s_4 \rightarrow s_2$.
\end{itemize}
%
Combined, these constraints yield seven valid crash schedules.
Besides the two trivial crash schedules $\vec{s} = \vec{\top}$ and $\vec{s} = \vec{\bot}$,
the other five crash schedules yield five distinct disk states:
% 0: (list (cons b2 #f) (cons b1 #f) (cons b4 #f) (cons b3 #f)) <-- all #f
% 1: (list (cons b2 #f) (cons b1 #t) (cons b4 #f) (cons b3 #f)) <-- only first log block
% 2: (list (cons b2 #t) (cons b1 #t) (cons b4 #f) (cons b3 #f)) <-- first log block + first superblock
% 3: (list (cons b2 #t) (cons b1 #t) (cons b4 #f) (cons b3 #t)) <-- first log block + first superblock + second log block
% 4: (list (cons b2 #f) (cons b1 #t) (cons b4 #f) (cons b3 #t)) <-- both log blocks
% 5: (list (cons b2 #t) (cons b1 #t) (cons b4 #t) (cons b3 #t)) <-- all #t
% 6: (list (cons b2 #f) (cons b1 #f) (cons b4 #f) (cons b3 #t)) <-- only second log block
\begin{enumerate}[label={\raisebox{2\baselineskip}[0pt][0pt]{(\arabic*)}},ref=(\arabic*)]
\item 
\begin{minipage}[b]{0.5\textwidth}
$[s_1 = \top, s_2 = \bot, s_3 = \bot, s_4 = \bot]$\\
(only the first log block is on disk) \\
\end{minipage}\quad%
\begin{minipage}{0.4\textwidth}
\vspace{-1.2em}
\includegraphics[width=\textwidth]{figs/sec3-1.pdf}
\end{minipage}
\label{sec:problem:loststate}
\item 
\begin{minipage}[b]{0.5\textwidth}
$[s_1 = \bot, s_2 = \bot, s_3 = \top, s_4 = \bot]$\\
(only the second log block is on disk) \\
\end{minipage}\quad%
\begin{minipage}{0.4\textwidth}
\vspace{-1.2em}
\includegraphics[width=\textwidth]{figs/sec3-2.pdf}
\end{minipage}

@@

\item 
\begin{minipage}[b]{0.5\textwidth}
$[s_1 = \top, s_2 = \top, s_3 = \top, s_4 = \bot]$\\
(the first log block, first superblock write, and second log block are on disk)
\end{minipage}\quad%
\begin{minipage}{0.4\textwidth}
\vspace{-1.2em}
\includegraphics[width=\textwidth]{figs/sec3-5.pdf}
\end{minipage}
\end{enumerate}
%
Each of these states satisfies the key-value store's crash-consistency predicate $\consistent{d}$
defined in \cref{s:overview},
as in each case the superblock's \texttt{head} and \texttt{tail} pointers
refer only to log blocks that are also on disk.
Some states result in data loss after the crash---%
for example, neither key can be retrieved from crash state \ref{sec:problem:loststate} above, as the superblock is empty---%
but these states are still consistent
(i.e., they satisfy the log's representation invariant).
This set of two rules therefore makes the \texttt{SingleEntry_TwoAppend} litmus test crash consistent according to \cref{def:crash-consistent}.

>>>>

\begin{example}\label{sec:problem:example}
  \normalfont
Consider the \texttt{SingleEntry_TwoAppend} litmus test from \cref{depsynth:s:overview}.
Interpreting the initial and main programs gives two traces:
%
\begin{align*}
    \interpret{P_\emph{initial}} &= [\texttt{write}(1, \texttt{to_block}((0, 42)), \langle \textsf{log}, 0 \rangle), \\
                                 &\quad\ \  \texttt{write}(0, \texttt{to_block}((1, 2)),  \langle \textsf{superblock}, 0 \rangle)] \\
    \interpret{P_\emph{main}}    &= [\texttt{write}(2, \texttt{to_block}((1, 81)), \langle \textsf{log}, 1 \rangle), \\
                                 &\quad\ \  \texttt{write}(0, \texttt{to_block}((1, 3)),  \langle \textsf{superblock}, 1 \rangle), \\
                                 &\quad\ \  \texttt{write}(3, \texttt{to_block}((2, 37)), \langle \textsf{log}, 2 \rangle), \\
                                 &\quad\ \  \texttt{write}(0, \texttt{to_block}((1, 4)),  \langle \textsf{superblock}, 2 \rangle)]
\end{align*}
%
Let $\vec{s} = [s_1, s_2, s_3, s_4]$ be a crash schedule for $P_\emph{main}$.
Applying the two synthesized rules from \cref{depsynth:s:overview}
restricts the valid crash schedules (\cref{def:valid-schedule}):
%
\begin{itemize}
\item $\deprule{\textsf{superblock}}{\textsf{log}}{=}$ requires $s_2 \rightarrow s_1$ and $s_4 \rightarrow s_3$.
\item $\deprule{\textsf{superblock}}{\textsf{superblock}}{>}$ requires $s_4 \rightarrow s_2$.
\end{itemize}
%
Combined, these constraints yield seven valid crash schedules.
Besides the two trivial crash schedules $\vec{s} = \vec{\top}$ and $\vec{s} = \vec{\bot}$,
the other five crash schedules yield five distinct disk states:
% 0: (list (cons b2 #f) (cons b1 #f) (cons b4 #f) (cons b3 #f)) <-- all #f
% 1: (list (cons b2 #f) (cons b1 #t) (cons b4 #f) (cons b3 #f)) <-- only first log block
% 2: (list (cons b2 #t) (cons b1 #t) (cons b4 #f) (cons b3 #f)) <-- first log block + first superblock
% 3: (list (cons b2 #t) (cons b1 #t) (cons b4 #f) (cons b3 #t)) <-- first log block + first superblock + second log block
% 4: (list (cons b2 #f) (cons b1 #t) (cons b4 #f) (cons b3 #t)) <-- both log blocks
% 5: (list (cons b2 #t) (cons b1 #t) (cons b4 #t) (cons b3 #t)) <-- all #t
% 6: (list (cons b2 #f) (cons b1 #f) (cons b4 #f) (cons b3 #t)) <-- only second log block
\begin{enumerate}[label={\raisebox{2\baselineskip}[0pt][0pt]{(\arabic*)}},ref=(\arabic*)]
\item 
\begin{minipage}[b]{0.5\textwidth}
$[s_1 = \top, s_2 = \bot, s_3 = \bot, s_4 = \bot]$\\
(only the first log block is on disk) \\
\end{minipage}\quad%
\begin{minipage}{0.4\textwidth}
\vspace{-1.2em}
\includegraphics[width=\textwidth]{figs/sec3-1.pdf}
\end{minipage}
\label{sec:problem:loststate}
\item 
\begin{minipage}[b]{0.5\textwidth}
$[s_1 = \bot, s_2 = \bot, s_3 = \top, s_4 = \bot]$\\
(only the second log block is on disk) \\
\end{minipage}\quad%
\begin{minipage}{0.4\textwidth}
\vspace{-1.2em}
\includegraphics[width=\textwidth]{figs/sec3-2.pdf}
\end{minipage}

@@

\item 
\begin{minipage}[b]{0.5\textwidth}
$[s_1 = \top, s_2 = \top, s_3 = \top, s_4 = \bot]$\\
(the first log block, first superblock write, and second log block are on disk)
\end{minipage}\quad%
\begin{minipage}{0.4\textwidth}
\vspace{-1.2em}
\includegraphics[width=\textwidth]{figs/sec3-5.pdf}
\end{minipage}
\end{enumerate}
%
Each of these states satisfies the key-value store's crash-consistency predicate $\consistent{d}$
defined in \cref{depsynth:s:overview},
as in each case the superblock's \texttt{head} and \texttt{tail} pointers
refer only to log blocks that are also on disk.
Some states result in data loss after the crash---%
for example, neither key can be retrieved from crash state \ref{sec:problem:loststate} above, as the superblock is empty---%
but these states are still consistent
(i.e., they satisfy the log's representation invariant).
This set of two rules therefore makes the \texttt{SingleEntry_TwoAppend} litmus test crash consistent according to \cref{def:crash-consistent}.

### 2023-05-15 chapters/depsynth/related.tex
acks, jitsynth, dmacros
Deambiguate section labels

\paragraph{Crash-consistency bug-finding tools.}
Ferrite~\cite{bornholt:ferrite} is a framework for specifying \emph{crash-consistency models},
which formally define the behavior of a storage system across crashes,
and for automatically finding violations of such models in a storage system implementation.
One way to specify these models is with litmus tests that demonstrate unintuitive behaviors;
\depsynth builds on this approach by automatically synthesizing rules from such litmus tests.
\depsynth also takes inspiration from Ferrite's synthesis tool
for inserting \texttt{fsync} calls into litmus tests to make them crash consistent,
but instead focuses on making the \emph{storage system itself} crash consistent
rather than the user code running on top of it.
CrashMonkey~\cite{mohan:crashmonkey} is a tool for finding crash-consistency bugs in Linux file systems.
CrashMonkey exhaustively enumerates all litmus tests with a given set of system calls,
runs them against the target file system,
and then tests each possible crash state for consistency.
Connecting CrashMonkey-like litmus test generation with \depsynth
could provide developers with a comprehensive set of litmus tests for their system for free,
lowering the burden of applying \depsynth.
FiSC~\cite{yang:fisc} and eXplode~\cite{yang:explode}
use model checking to find bugs in storage systems.

One advantage of bug-finding tools is that they are significantly easier to apply to production systems
than heavyweight verification tools.
\cite{bornholt:s3} describe the use of lightweight formal methods
to validate the crash consistency (and other properties)
of ShardStore, a key-value store for Amazon S3.
Their approach applies property-based testing to automatically find and minimize litmus tests
that demonstrate crash-consistency issues.
\depsynth takes this idea one step further by automatically \emph{fixing} such issues once they are found.

>>>>

\paragraph{Crash-consistency bug-finding tools.}
Ferrite~\cite{bornholt:ferrite} is a framework for specifying \emph{crash-consistency models},
which formally define the behavior of a storage system across crashes,
and for automatically finding violations of such models in a storage system implementation.
One way to specify these models is with litmus tests that demonstrate unintuitive behaviors;
\depsynth builds on this approach by automatically synthesizing rules from such litmus tests.
\depsynth also takes inspiration from Ferrite's synthesis tool
for inserting \texttt{fsync} calls into litmus tests to make them crash consistent,
but instead focuses on making the \emph{storage system itself} crash consistent
rather than the user code running on top of it.
CrashMonkey~\cite{mohan:crashmonkey} is a tool for finding crash-consistency bugs in Linux file systems.
Chipmunk~\cite{leblanc:chipmunk} extends the CrashMonkey approach to persistent-memory file systems
by exploring finer-grained crash states to account for the byte-addressable nature of non-volatile memory.
CrashMonkey exhaustively enumerates all litmus tests with a given set of system calls,
runs them against the target file system,
and then tests each possible crash state for consistency.
Connecting CrashMonkey-like litmus test generation with \depsynth
could provide developers with a comprehensive set of litmus tests for their system for free,
lowering the burden of applying \depsynth.
To give stronger coverage guarantees that do not depend on enumerating litmus tests,
FiSC~\cite{yang:fisc} and eXplode~\cite{yang:explode}
use model checking to find bugs in storage systems.

One advantage of bug-finding tools is that they are significantly easier to apply to production systems
than heavyweight verification tools.
Bornholt et al. \cite{bornholt:s3} describe the use of lightweight formal methods
to validate the crash consistency (and other properties)
of ShardStore, the Amazon S3 storage node that we study in Section~\ref{sec:eval:shardstore}.
Their approach applies property-based testing to automatically find and minimize litmus tests
that demonstrate crash-consistency issues.
\depsynth takes this idea one step further by automatically \emph{fixing} such issues once they are found.

### 2023-05-15 chapters/depsynth/results.tex
Deambiguate section labels

To show that developers can use \depsynth to build realistic storage systems, 
%instead of writing their own manual crash-consistency implementation,
we implemented a key-value store that follows the design of \shardstore%
\footnote{Anonymized for double-blind review.}~%
\cite{bornholt:s3-anon},
a key-value store operating in production for a major commercial cloud object storage service.

>>>>

To show that developers can use \depsynth to build realistic storage systems, 
%instead of writing their own manual crash-consistency implementation,
we implemented a key-value store that follows the design of \shardstore~\cite{bornholt:s3},
the exabyte-scale production storage node for the Amazon S3 object storage service.

### 2023-05-15 chapters/depsynth/synthesis.tex
Deambiguate section labels

\begin{example}\label{sec:alg:example}
Consider running \rulesfortest for the simple log-structured key-value store
and \texttt{SingleEntry_TwoAppend} litmus test from \cref{s:overview}.
From \cref{sec:problem:example} we know that this test produces a set \wr of four writes:
%
\begin{align*}
    w_1 &= \texttt{write}(2, \texttt{to_block}((1, 81)), \langle \textsf{log}, 1 \rangle), \\
    w_2 &= \texttt{write}(0, \texttt{to_block}((1, 3)),  \langle \textsf{superblock}, 1 \rangle), \\
    w_3 &= \texttt{write}(3, \texttt{to_block}((2, 37)), \langle \textsf{log}, 2 \rangle), \\
    w_4 &= \texttt{write}(0, \texttt{to_block}((1, 4)),  \langle \textsf{superblock}, 2 \rangle)
\end{align*}
%
\phaseone first chooses the first write to add to the total order.
Suppose it chooses $w_2$.
This choice results in the following graph \gr at line~\ref{fig:rules:phase1angelic}
(shaded nodes are in \ord; white nodes are in \wr):
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-1.pdf}\end{center}
%
The check at line~\ref{fig:rules:phase1sufficient}
finds that this graph is not crash consistent: it allows a crash schedule where $w_2$ is on disk but no other writes are,
which violates the crash-consistency predicate as $w_2$ is a superblock write pointing to a log block that is not on disk.
\phaseone therefore continues (line~\ref{fig:rules:phase1continue}),
which prunes any total order that starts with $[w_2]$ from the search,
and chooses a next write to consider, say $w_3$.
The total order starting with $[w_3]$ does pass the crash consistency check,
so \phaseone recurses with $\ord = [w_3]$ and $\wr = \{w_1, w_2, w_4\}$.
In this recursive call,
suppose we again first choose $w_2$ to add to the total order.
This choice results in the following graph \gr:
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-2.pdf}\end{center}
%
Again, line~\ref{fig:rules:phase1sufficient} finds that this graph is not crash consistent,
for the same reason as before (superblock write $w_2$ can be on disk when log write $w_1$ is not),
and so the search continues, pruning any total order that starts with $[w_3, w_2]$.
Suppose it next chooses $w_1$ to add to the total order.
This choice succeeds, making the recursive call with $\ord = [w_3, w_1]$ and $\wr = \{w_2, w_4\}$.
From here, any choice \phaseone makes will succeed.
Supposing it choses $w_2$ first,
\phaseone eventually reaches line~\ref{fig:rules:phase1tophase2} and continues to \phasetwo
with the following initial graph \gr:
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-3.pdf}\end{center}

\phasetwo proceeds by trying to remove one edge at a time from \gr.
Suppose it first chooses to remove edge $(w_3, w_1)$,
and so recurses at line~\ref{fig:rules:phase2recurse} on the graph $\gr' = \gr \setminus \{(w_3, w_1)\}$.
This graph still ensures crash consistency at line~\ref{fig:rules:phase2sufficient},
as writing $w_1$ before $w_3$ does not affect consistency.
The recursion can continue twice more
by choosing and successfully removing edges $(w_3, w_2)$ and then $(w_1, w_4)$ as well,
eventually reaching line~\ref{fig:rules:phase2loop} with the following graph \gr (now with write labels shown):\tighten
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-4.pdf}\end{center}
%
From here, the loop in \phasetwo now tries to remove each of the three remaining edges,
but each attempted $\gr'$ violates crash consistency and so returns $\bot$ from the next recursive call.
\phasetwo therefore exits the loop with the above graph \gr,
which we now know is minimal as no further edges can be removed.
Applying \rulesforgraph to \gr yields the two rules from \cref{s:overview}:
\begin{align*}
    \deprule{\textsf{superblock}&}{\textsf{log}}{=} & \text{ from edges } (w_3, w_4) \text{ and } (w_1, w_2) \\
    \deprule{\textsf{superblock}&}{\textsf{superblock}}{>} & \text{ from edge } (w_2, w_4).
\end{align*}
\end{example}

>>>>

\begin{example}\label{sec:alg:example}
  \normalfont
Consider running \rulesfortest for the simple log-structured key-value store
and \texttt{SingleEntry_TwoAppend} litmus test from \cref{depsynth:s:overview}.
From \cref{sec:problem:example} we know that this test produces a set \wr of four writes:
%
\begin{align*}
    w_1 &= \texttt{write}(2, \texttt{to_block}((1, 81)), \langle \textsf{log}, 1 \rangle), \\
    w_2 &= \texttt{write}(0, \texttt{to_block}((1, 3)),  \langle \textsf{superblock}, 1 \rangle), \\
    w_3 &= \texttt{write}(3, \texttt{to_block}((2, 37)), \langle \textsf{log}, 2 \rangle), \\
    w_4 &= \texttt{write}(0, \texttt{to_block}((1, 4)),  \langle \textsf{superblock}, 2 \rangle)
\end{align*}
%
\phaseone first chooses the first write to add to the total order.
Suppose it chooses $w_2$.
This choice results in the following graph \gr at line~\ref{fig:rules:phase1angelic}
(shaded nodes are in \ord; white nodes are in \wr):
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-1.pdf}\end{center}
%
The check at line~\ref{fig:rules:phase1sufficient}
finds that this graph is not crash consistent: it allows a crash schedule where $w_2$ is on disk but no other writes are,
which violates the crash-consistency predicate as $w_2$ is a superblock write pointing to a log block that is not on disk.
\phaseone therefore continues (line~\ref{fig:rules:phase1continue}),
which prunes any total order that starts with $[w_2]$ from the search,
and chooses a next write to consider, say $w_3$.
The total order starting with $[w_3]$ does pass the crash consistency check,
so \phaseone recurses with $\ord = [w_3]$ and $\wr = \{w_1, w_2, w_4\}$.
In this recursive call,
suppose we again first choose $w_2$ to add to the total order.
This choice results in the following graph \gr:
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-2.pdf}\end{center}
%
Again, line~\ref{fig:rules:phase1sufficient} finds that this graph is not crash consistent,
for the same reason as before (superblock write $w_2$ can be on disk when log write $w_1$ is not),
and so the search continues, pruning any total order that starts with $[w_3, w_2]$.
Suppose it next chooses $w_1$ to add to the total order.
This choice succeeds, making the recursive call with $\ord = [w_3, w_1]$ and $\wr = \{w_2, w_4\}$.
From here, any choice \phaseone makes will succeed.
Supposing it choses $w_2$ first,
\phaseone eventually reaches line~\ref{fig:rules:phase1tophase2} and continues to \phasetwo
with the following initial graph \gr:
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-3.pdf}\end{center}

\phasetwo proceeds by trying to remove one edge at a time from \gr.
Suppose it first chooses to remove edge $(w_3, w_1)$,
and so recurses at line~\ref{fig:rules:phase2recurse} on the graph $\gr' = \gr \setminus \{(w_3, w_1)\}$.
This graph still ensures crash consistency at line~\ref{fig:rules:phase2sufficient},
as writing $w_1$ before $w_3$ does not affect consistency.
The recursion can continue twice more
by choosing and successfully removing edges $(w_3, w_2)$ and then $(w_1, w_4)$ as well,
eventually reaching line~\ref{fig:rules:phase2loop} with the following graph \gr (now with write labels shown):\tighten
%
\begin{center}\includegraphics[width=0.5\textwidth]{figs/sec4-4.pdf}\end{center}
%
From here, the loop in \phasetwo now tries to remove each of the three remaining edges,
but each attempted $\gr'$ violates crash consistency and so returns $\bot$ from the next recursive call.
\phasetwo therefore exits the loop with the above graph \gr,
which we now know is minimal as no further edges can be removed.
Applying \rulesforgraph to \gr yields the two rules from \cref{depsynth:s:overview}:
\begin{align*}
    \deprule{\textsf{superblock}&}{\textsf{log}}{=} & \text{ from edges } (w_3, w_4) \text{ and } (w_1, w_2) \\
    \deprule{\textsf{superblock}&}{\textsf{superblock}}{>} & \text{ from edge } (w_2, w_4).
\end{align*}
\end{example}

### 2023-05-15 chapters/jitsynth/impl.tex
Deambiguate section labels

\section{Implementation}\label{s:impl}
We implemented \jitsynth as described in \autoref{s:overview} using
Rosette~\cite{torlak:rosette} as our host language.
%Without bounding the length of the compiler, the space explored by \jitsynth is infinite, so we use a timeout
%of 48 hours to bound execution.
Since the search spaces for different compiler lengths are disjoint,
the \jitsynth implementation searches these spaces in parallel~\cite{bornholt:synapse}.
%In addition, \jitsynth implements several optimizations
%in order to synthesize real-world JIT compilers, as follows.
%
%
%\paragraph{ARM Fuel Function.}
%For simplicity,
We use $\Phi(\vec{p}) = \texttt{length}(\vec{p})$ as the fuel function for all
languages studied in this paper. This provides sufficient fuel for evaluating
programs in these languages that are accepted by the OS kernel. For example, the
Linux kernel requires eBPF programs to be loop-free, and it enforces this
restriction with a conservative static check; programs that fail the check are
not passed to the JIT~\cite{gershuni:crab-ebpf}.

>>>>

\section{Implementation}\label{jitsynth:s:impl}
We implemented \jitsynth as described in \autoref{jitsynth:s:overview} using
Rosette~\cite{torlak:rosette} as our host language.
%Without bounding the length of the compiler, the space explored by \jitsynth is infinite, so we use a timeout
%of 48 hours to bound execution.
Since the search spaces for different compiler lengths are disjoint,
the \jitsynth implementation searches these spaces in parallel~\cite{bornholt:synapse}.
%In addition, \jitsynth implements several optimizations
%in order to synthesize real-world JIT compilers, as follows.
%
%
%\paragraph{ARM Fuel Function.}
%For simplicity,
We use $\Phi(\vec{p}) = \texttt{length}(\vec{p})$ as the fuel function for all
languages studied in this paper. This provides sufficient fuel for evaluating
programs in these languages that are accepted by the OS kernel. For example, the
Linux kernel requires eBPF programs to be loop-free, and it enforces this
restriction with a conservative static check; programs that fail the check are
not passed to the JIT~\cite{gershuni:crab-ebpf}.

### 2023-05-15 chapters/jitsynth/search.tex
Deambiguate section labels

The space of such programs is intractably large, however, even for small inputs.
For instance, it includes at least $2^{350}$ programs of length $k=5$ and depth
$d\leq 3$ for the toy example from \autoref{s:overview}. \jitsynth therefore
employs two effective heuristics to direct the exploration of this space toward
the most promising candidates first, as defined by the read-write and pre-load
sketches.\tighten

@@

The read-write sketch, $\RW(k, d, \iota, \arm_S, \arm_T, \Map)$, is based on the
observation that many practical source and target languages provide similar
functionality, so a source instruction $\iota$ can often be emulated with target
instructions that access the same parts of the state as $\iota$. For example,
the \cc{addi32} instruction from eBPF reads and writes only registers (not,
e.g., memory), and it can be emulated with RISC-V instructions that also touch
only registers (\autoref{s:overview}). Moreover, note that the semantics of
\cc{addi32} ignores the values of its $\mathid{src}$ and $\mathid{off}$
fields, and that the target RISC-V instructions do the same. Based on these
observations, our optimized sketch for \cc{addi32} would therefore consists of
instruction holes that allow only register-register instructions, with field
holes that exclude $\mathid{src}$ and $\mathid{off}$. We first formalize this
intuition with the notion of \emph{read and write sets}, and then describe how \jitsynth
applies such sets to create \RW sketches.\tighten

@@

\jitsynth computes all read and write sets from their definitions, by using the
host symbolic evaluator to reduce the reasoning about instruction semantics to
SMT queries. This reduction is possible because we assume that all ARM
interpreters are self-finitizing, as discussed in \autoref{s:overview}.

>>>>

The space of such programs is intractably large, however, even for small inputs.
For instance, it includes at least $2^{350}$ programs of length $k=5$ and depth
$d\leq 3$ for the toy example from \autoref{jitsynth:s:overview}. \jitsynth therefore
employs two effective heuristics to direct the exploration of this space toward
the most promising candidates first, as defined by the read-write and pre-load
sketches.\tighten

@@

The read-write sketch, $\RW(k, d, \iota, \arm_S, \arm_T, \Map)$, is based on the
observation that many practical source and target languages provide similar
functionality, so a source instruction $\iota$ can often be emulated with target
instructions that access the same parts of the state as $\iota$. For example,
the \cc{addi32} instruction from eBPF reads and writes only registers (not,
e.g., memory), and it can be emulated with RISC-V instructions that also touch
only registers (\autoref{jitsynth:s:overview}). Moreover, note that the semantics of
\cc{addi32} ignores the values of its $\mathid{src}$ and $\mathid{off}$
fields, and that the target RISC-V instructions do the same. Based on these
observations, our optimized sketch for \cc{addi32} would therefore consists of
instruction holes that allow only register-register instructions, with field
holes that exclude $\mathid{src}$ and $\mathid{off}$. We first formalize this
intuition with the notion of \emph{read and write sets}, and then describe how \jitsynth
applies such sets to create \RW sketches.\tighten

@@

\jitsynth computes all read and write sets from their definitions, by using the
host symbolic evaluator to reduce the reasoning about instruction semantics to
SMT queries. This reduction is possible because we assume that all ARM
interpreters are self-finitizing, as discussed in \autoref{jitsynth:s:overview}.
